---
title: "behavioral_analysis_RSA_plots"
output: html_document
---

```{r, SETTINGS-knitr, include=FALSE}
stopifnot(require(knitr))
options(width = 90)
opts_chunk$set(
  cache = TRUE,
  comment = NA,
  message = FALSE,
  warning = FALSE
)
```

Load required packages:
```{r}
library(rethinking)
library(bayestestR)
library(brms)
options(mc.cores = parallel::detectCores())
library(tidyverse)
theme_set(theme_default())
library(readr)
library(tidyr)
library(Hmisc)
library(plyr)
library(RColorBrewer)
library(reshape2)

```


## Count data model (aggregated binomial regression model)

Load the data:
```{r}

setwd("/Users/lennart/Desktop/savage/github/csv_data/") #change working dir
#setwd("/.../csv_data/") #change working dir

ds = read.csv("savage_long.csv")  # read from first sheet
n_sub <- 49
  
ds[,'SubID']<-factor(ds[,'SubID'])
head(ds, 10)

conditions <- make_conditions(ds, "SubID")

#wide format

ds_wide = read.csv("savage_wide.csv")

#rsa data
ds_rsa = read.csv("rsa.csv")
ds_rsa_norm = read.csv("rsa_norm.csv")

#decoding data
ds_decoding = read.csv("decoding.csv")

ds_decoding1 = read.csv("decoding1.csv")
ds_decoding2 = read.csv("decoding2.csv")

#behavioral sample
ds_behav = ds[ which(ds$ofc_acc =='NaN'),]
ds_behav_wide = ds_wide[ 1:20,]
  
#fmri sample
ds_fmri = ds[ 81:196,]
ds_fmri_wide = ds_wide[ 21:49,]

```


###ROPE for CS1 decisions using grid approximation

```{r}
# select variables 
new_ds<- ds[ which(ds$CS =='1'), ]

n_choices = sum(new_ds$choices)

total_choices = sum(new_ds$total_choices)

rel_choices <- n_choices/total_choices

rel_choices*12

indiv_choice = new_ds$choices/new_ds$total_choices
indiv_choice
#grid approximation
p_grid <- seq( from=0 , to=1 , length.out=1e4 )

#mildly informative prior centered at 0.5
prior <- rnorm( 1e4, .5, .1 )
dens( prior , xlab="prior probability of choosing CS1+", xlim=c(0,1))

likelihood <- dbinom( n_choices , size=total_choices , prob=p_grid )
unstd_posterior <- prior * likelihood
posterior <- unstd_posterior / sum(unstd_posterior)

plot( likelihood )

#sampling from posterior distribution
samples <- sample( p_grid , prob=posterior , size=1e5 , replace=TRUE )
samples_CS1 <- samples

#how much posterior density between 0.45 and 0.55 (ROPE)
mean(samples >= 0.45 & samples <= 0.55)

#high-probability density interval
HDI <- HPDI(samples, prob=.89)

HDI1 <- HDI
HDI1
#find the proportion of the HPDI that is inside the ROPE
rope(samples, range = c(.45, .55))

#credible interval
quantile(samples, c(0.025, 0.975))

plot( samples )
dens( samples , xlab="probability of choosing CS1+", show.HPDI=.89, xlim=c(0,1))
#add HPDI
#abline(v = HDI, col = "blue")
#add ROPE
abline(v = c(0.45, 0.55), col = "red")

#MAP
p_grid[ which.max(posterior) ]

mean( samples )
median( samples )

#simulate from posterior --> posterior predictive distribution
dummy_d <- rbinom( 1e5 , size=12 , prob=samples)

simplehist( dummy_d, xlab="simulated choices of CS1+" , xlim=c(0,12))


precis( samples ) 


```

###ROPE for CS1 decisions using grid approximation - fmri sample

```{r}
# select variables 
new_ds<- ds_fmri[ which(ds_fmri$CS =='1'), ]

n_choices = sum(new_ds$choices)

total_choices = sum(new_ds$total_choices)

rel_choices <- n_choices/total_choices

rel_choices*12

indiv_choice = new_ds$choices/new_ds$total_choices
indiv_choice
#grid approximation
p_grid <- seq( from=0 , to=1 , length.out=1e4 )

#mildly informative prior centered at 0.5
prior <- rnorm( 1e4, .5, .1 )
dens( prior , xlab="prior probability of choosing CS1+", xlim=c(0,1))

likelihood <- dbinom( n_choices , size=total_choices , prob=p_grid )
unstd_posterior <- prior * likelihood
posterior <- unstd_posterior / sum(unstd_posterior)

plot( likelihood )

#sampling from posterior distribution
samples <- sample( p_grid , prob=posterior , size=1e5 , replace=TRUE )
samples_CS1 <- samples

#how much posterior density between 0.45 and 0.55 (ROPE)
mean(samples >= 0.45 & samples <= 0.55)

#high-probability density interval
HDI <- HPDI(samples, prob=.89)

HDI1 <- HDI
HDI1
#find the proportion of the HPDI that is inside the ROPE
rope(samples, range = c(.45, .55))

#credible interval
quantile(samples, c(0.025, 0.975))

plot( samples )
dens( samples , xlab="probability of choosing CS1+", show.HPDI=.89, xlim=c(0,1))
#add HPDI
#abline(v = HDI, col = "blue")
#add ROPE
abline(v = c(0.45, 0.55), col = "red")

#MAP
p_grid[ which.max(posterior) ]

mean( samples )
median( samples )


#simulate from posterior --> posterior predictive distribution
dummy_d <- rbinom( 1e5 , size=12 , prob=samples)

simplehist( dummy_d, xlab="simulated choices of CS1+" , xlim=c(0,12))


precis( samples ) 


```
###ROPE for CS1 decisions using grid approximation - behav sample

```{r}
# select variables 
new_ds<- ds_behav[ which(ds_behav$CS =='1'), ]

n_choices = sum(new_ds$choices)

total_choices = sum(new_ds$total_choices)

rel_choices <- n_choices/total_choices

rel_choices*12

indiv_choice = new_ds$choices/new_ds$total_choices
indiv_choice
#grid approximation
p_grid <- seq( from=0 , to=1 , length.out=1e4 )

#mildly informative prior centered at 0.5
prior <- rnorm( 1e4, .5, .1 )
dens( prior , xlab="prior probability of choosing CS1+", xlim=c(0,1))

likelihood <- dbinom( n_choices , size=total_choices , prob=p_grid )
unstd_posterior <- prior * likelihood
posterior <- unstd_posterior / sum(unstd_posterior)

plot( likelihood )

#sampling from posterior distribution
samples <- sample( p_grid , prob=posterior , size=1e5 , replace=TRUE )
samples_CS1 <- samples

#how much posterior density between 0.45 and 0.55 (ROPE)
mean(samples >= 0.45 & samples <= 0.55)

#high-probability density interval
HDI <- HPDI(samples, prob=.89)

HDI1 <- HDI
HDI1
#find the proportion of the HPDI that is inside the ROPE
rope(samples, range = c(.45, .55))

#credible interval
quantile(samples, c(0.025, 0.975))

plot( samples )
dens( samples , xlab="probability of choosing CS1+", show.HPDI=.89, xlim=c(0,1))
#add HPDI
#abline(v = HDI, col = "blue")
#add ROPE
abline(v = c(0.45, 0.55), col = "red")

#MAP
p_grid[ which.max(posterior) ]

mean( samples )
median( samples )


#simulate from posterior --> posterior predictive distribution
dummy_d <- rbinom( 1e5 , size=12 , prob=samples)

simplehist( dummy_d, xlab="simulated choices of CS1+" , xlim=c(0,12))


precis( samples ) 


```



###ROPE for CS2 decisions using grid approximation

```{r}
# select variables 
new_ds<- ds[ which(ds$CS =='2'), ]

n_choices = sum(new_ds$choices)

total_choices = sum(new_ds$total_choices)

rel_choices <- n_choices/total_choices

rel_choices*12

#grid approximation
p_grid <- seq( from=0 , to=1 , length.out=1e4 )

#mildly informative prior centered at 0.5
prior <- rnorm( 1e4, .5, .1 )
dens( prior , xlab="prior probability of choosing CS2+", xlim=c(0,1))

likelihood <- dbinom( n_choices , size=total_choices , prob=p_grid )
unstd_posterior <- prior * likelihood
posterior <- unstd_posterior / sum(unstd_posterior)

#sampling from posterior distribution
samples <- sample( p_grid , prob=posterior , size=1e5 , replace=TRUE )
samples_CS2 <- samples

#how much posterior density between 0.45 and 0.55 (ROPE)
mean(samples >= 0.45 & samples <= 0.55)

#highest-posterior density interval
HDI <- HPDI(samples, prob=.89)

HDI2 <- HDI
HDI2
#find the proportion of the HPDI that is inside the ROPE
rope(samples, range = c(.45, .55))

#credible interval
quantile(samples, c(0.025, 0.975))

plot( samples )
dens( samples , xlab="probability of choosing CS2+", show.HPDI=.89, xlim=c(0,1))
#add HPDI
#abline(v = HDI, col = "blue")
#add ROPE
abline(v = c(0.45, 0.55), col = "red")


#MAP
p_grid[ which.max(posterior) ]

mean( samples )
median( samples )

#simulate from posterior --> posterior predictive distribution
dummy_d <- rbinom( 1e5 , size=12 , prob=samples)
simplehist( dummy_d , xlab="simulated choices of CS2+" , xlim=c(0,12))
```

###ROPE for CS2 decisions using grid approximation - fmri sample

```{r}
# select variables 
new_ds<- ds_fmri[ which(ds_fmri$CS =='2'), ]

n_choices = sum(new_ds$choices)

total_choices = sum(new_ds$total_choices)

rel_choices <- n_choices/total_choices

rel_choices*12

#grid approximation
p_grid <- seq( from=0 , to=1 , length.out=1e4 )

#mildly informative prior centered at 0.5
prior <- rnorm( 1e4, .5, .1 )
dens( prior , xlab="prior probability of choosing CS2+", xlim=c(0,1))

likelihood <- dbinom( n_choices , size=total_choices , prob=p_grid )
unstd_posterior <- prior * likelihood
posterior <- unstd_posterior / sum(unstd_posterior)

#sampling from posterior distribution
samples <- sample( p_grid , prob=posterior , size=1e5 , replace=TRUE )
samples_CS2 <- samples

#how much posterior density between 0.45 and 0.55 (ROPE)
mean(samples >= 0.45 & samples <= 0.55)

#highest-posterior density interval
HDI <- HPDI(samples, prob=.89)

HDI2 <- HDI
HDI2
#find the proportion of the HPDI that is inside the ROPE
rope(samples, range = c(.45, .55))

#credible interval
quantile(samples, c(0.025, 0.975))

plot( samples )
dens( samples , xlab="probability of choosing CS2+", show.HPDI=.89, xlim=c(0,1))
#add HPDI
#abline(v = HDI, col = "blue")
#add ROPE
abline(v = c(0.45, 0.55), col = "red")


#MAP
p_grid[ which.max(posterior) ]

mean( samples )
median( samples )


#simulate from posterior --> posterior predictive distribution
dummy_d <- rbinom( 1e5 , size=12 , prob=samples)
simplehist( dummy_d , xlab="simulated choices of CS2+" , xlim=c(0,12))
```
###ROPE for CS2 decisions using grid approximation - behav sample

```{r}
# select variables 
new_ds<- ds_behav[ which(ds_behav$CS =='2'), ]

n_choices = sum(new_ds$choices)

total_choices = sum(new_ds$total_choices)

rel_choices <- n_choices/total_choices

rel_choices*12

#grid approximation
p_grid <- seq( from=0 , to=1 , length.out=1e4 )

#mildly informative prior centered at 0.5
prior <- rnorm( 1e4, .5, .1 )
dens( prior , xlab="prior probability of choosing CS2+", xlim=c(0,1))

likelihood <- dbinom( n_choices , size=total_choices , prob=p_grid )
unstd_posterior <- prior * likelihood
posterior <- unstd_posterior / sum(unstd_posterior)

#sampling from posterior distribution
samples <- sample( p_grid , prob=posterior , size=1e5 , replace=TRUE )
samples_CS2 <- samples

#how much posterior density between 0.45 and 0.55 (ROPE)
mean(samples >= 0.45 & samples <= 0.55)

#highest-posterior density interval
HDI <- HPDI(samples, prob=.89)

HDI2 <- HDI
HDI2
#find the proportion of the HPDI that is inside the ROPE
rope(samples, range = c(.45, .55))

#credible interval
quantile(samples, c(0.025, 0.975))

plot( samples )
dens( samples , xlab="probability of choosing CS2+", show.HPDI=.89, xlim=c(0,1))
#add HPDI
#abline(v = HDI, col = "blue")
#add ROPE
abline(v = c(0.45, 0.55), col = "red")


#MAP
p_grid[ which.max(posterior) ]

mean( samples )
median( samples )


#simulate from posterior --> posterior predictive distribution
dummy_d <- rbinom( 1e5 , size=12 , prob=samples)
simplehist( dummy_d , xlab="simulated choices of CS2+" , xlim=c(0,12))
```


###ROPE for CS1n decisions using grid approximation 

```{r}
# select variables 
new_ds<- ds[ which(ds$CS =='3'), ]

n_choices = sum(new_ds$choices)

total_choices = sum(new_ds$total_choices)

rel_choices <- n_choices/total_choices

rel_choices*12

#grid approximation
p_grid <- seq( from=0 , to=1 , length.out=1e4 )

#mildly informative prior centered at 0.5
prior <- rnorm( 1e4, .5, .1 )
dens( prior , xlab="prior probability of choosing CS1n", xlim=c(0,1))

likelihood <- dbinom( n_choices , size=total_choices , prob=p_grid )
unstd_posterior <- prior * likelihood
posterior <- unstd_posterior / sum(unstd_posterior)

#sampling from posterior distribution
samples <- sample( p_grid , prob=posterior , size=1e5 , replace=TRUE )

#how much posterior density between 0.45 and 0.55 (ROPE)
mean(samples >= 0.45 & samples <= 0.55)

#highest-posterior density interval
HDI <- HPDI(samples, prob=.89)

HDI3 <- HDI
HDI3

#find the proportion of the HPDI that is inside the ROPE
rope(samples, range = c(.45, .55))

#credible interval
quantile(samples, c(0.025, 0.975))

plot( samples )
dens( samples , xlab="probability of choosing CS1n", show.HPDI=.89, xlim=c(0,1))
#add HPDI
#abline(v = HDI, col = "blue")
#add ROPE
abline(v = c(0.45, 0.55), col = "red")

#MAP
p_grid[ which.max(posterior) ]

mean( samples )
median( samples )

#simulate from posterior --> posterior predictive distribution
dummy_d <- rbinom( 1e5 , size=12 , prob=samples)
simplehist( dummy_d , xlab="simulated choices of CS1n" , xlim=c(0,12))
```

###ROPE for CS1n decisions using grid approximation - fmri sample

```{r}
# select variables 
new_ds<- ds_fmri[ which(ds_fmri$CS =='3'), ]

n_choices = sum(new_ds$choices)

total_choices = sum(new_ds$total_choices)

rel_choices <- n_choices/total_choices

rel_choices*12

#grid approximation
p_grid <- seq( from=0 , to=1 , length.out=1e4 )

#mildly informative prior centered at 0.5
prior <- rnorm( 1e4, .5, .1 )
dens( prior , xlab="prior probability of choosing CS1n", xlim=c(0,1))

likelihood <- dbinom( n_choices , size=total_choices , prob=p_grid )
unstd_posterior <- prior * likelihood
posterior <- unstd_posterior / sum(unstd_posterior)

#sampling from posterior distribution
samples <- sample( p_grid , prob=posterior , size=1e5 , replace=TRUE )

#how much posterior density between 0.45 and 0.55 (ROPE)
mean(samples >= 0.45 & samples <= 0.55)

#highest-posterior density interval
HDI <- HPDI(samples, prob=.89)

HDI3 <- HDI
HDI3
#find the proportion of the HPDI that is inside the ROPE
rope(samples, range = c(.45, .55))

#credible interval
quantile(samples, c(0.025, 0.975))

plot( samples )
dens( samples , xlab="probability of choosing CS1n", show.HPDI=.89, xlim=c(0,1))
#add HPDI
#abline(v = HDI, col = "blue")
#add ROPE
abline(v = c(0.45, 0.55), col = "red")

#MAP
p_grid[ which.max(posterior) ]

mean( samples )
median( samples )

#simulate from posterior --> posterior predictive distribution
dummy_d <- rbinom( 1e5 , size=12 , prob=samples)
simplehist( dummy_d , xlab="simulated choices of CS1n" , xlim=c(0,12))
```
###ROPE for CS1n decisions using grid approximation - behav sample

```{r}
# select variables 
new_ds<- ds_behav[ which(ds_behav$CS =='3'), ]

n_choices = sum(new_ds$choices)

total_choices = sum(new_ds$total_choices)

rel_choices <- n_choices/total_choices

rel_choices*12

#grid approximation
p_grid <- seq( from=0 , to=1 , length.out=1e4 )

#mildly informative prior centered at 0.5
prior <- rnorm( 1e4, .5, .1 )
dens( prior , xlab="prior probability of choosing CS1n", xlim=c(0,1))

likelihood <- dbinom( n_choices , size=total_choices , prob=p_grid )
unstd_posterior <- prior * likelihood
posterior <- unstd_posterior / sum(unstd_posterior)

#sampling from posterior distribution
samples <- sample( p_grid , prob=posterior , size=1e5 , replace=TRUE )

#how much posterior density between 0.45 and 0.55 (ROPE)
mean(samples >= 0.45 & samples <= 0.55)

#highest-posterior density interval
HDI <- HPDI(samples, prob=.89)

HDI3 <- HDI
HDI3
#find the proportion of the HPDI that is inside the ROPE
rope(samples, range = c(.45, .55))

#credible interval
quantile(samples, c(0.025, 0.975))

plot( samples )
dens( samples , xlab="probability of choosing CS1n", show.HPDI=.89, xlim=c(0,1))
#add HPDI
#abline(v = HDI, col = "blue")
#add ROPE
abline(v = c(0.45, 0.55), col = "red")

#MAP
p_grid[ which.max(posterior) ]

mean( samples )
median( samples )


#simulate from posterior --> posterior predictive distribution
dummy_d <- rbinom( 1e5 , size=12 , prob=samples)
simplehist( dummy_d , xlab="simulated choices of CS1n" , xlim=c(0,12))
```

###ROPE for CS2n decisions using grid approximation

```{r}
# select variables 
new_ds<- ds[ which(ds$CS =='4'), ]

n_choices = sum(new_ds$choices)

total_choices = sum(new_ds$total_choices)

rel_choices <- n_choices/total_choices

rel_choices*12

#grid approximation
p_grid <- seq( from=0 , to=1 , length.out=1e4 )

#mildly informative prior centered at 0.5
prior <- rnorm( 1e4, .5, .1 )
dens( prior , xlab="prior probability of choosing CS2n", xlim=c(0,1))

likelihood <- dbinom( n_choices , size=total_choices , prob=p_grid )
unstd_posterior <- prior * likelihood
posterior <- unstd_posterior / sum(unstd_posterior)

#sampling from posterior distribution
samples <- sample( p_grid , prob=posterior , size=1e5 , replace=TRUE )

#how much posterior density between 0.45 and 0.55 (ROPE)
mean(samples >= 0.45 & samples <= 0.55)

#highest-posterior density interval
HDI <- HPDI(samples, prob=.89)

HDI4 <- HDI
HDI4 

#find the proportion of the HPDI that is inside the ROPE
rope(samples, range = c(.45, .55))

#credible interval
quantile(samples, c(0.025, 0.975))

plot( samples )
dens( samples , xlab="probability of choosing CS2n", show.HPDI=.89, xlim=c(0,1))
#add HPDI
#abline(v = HDI, col = "blue")
#add ROPE
abline(v = c(0.45, 0.55), col = "red")

#MAP
p_grid[ which.max(posterior) ]

mean( samples )
median( samples )


#simulate from posterior --> posterior predictive distribution
dummy_d <- rbinom( 1e5 , size=12 , prob=samples)
simplehist( dummy_d , xlab="simulated choices of CS2n" , xlim=c(0,12))
```

###ROPE for CS2n decisions using grid approximation - fmri sample

```{r}
# select variables 
new_ds<- ds_fmri[ which(ds_fmri$CS =='4'), ]

n_choices = sum(new_ds$choices)

total_choices = sum(new_ds$total_choices)

rel_choices <- n_choices/total_choices

rel_choices*12

#grid approximation
p_grid <- seq( from=0 , to=1 , length.out=1e4 )

#mildly informative prior centered at 0.5
prior <- rnorm( 1e4, .5, .1 )
dens( prior , xlab="prior probability of choosing CS2n", xlim=c(0,1))

likelihood <- dbinom( n_choices , size=total_choices , prob=p_grid )
unstd_posterior <- prior * likelihood
posterior <- unstd_posterior / sum(unstd_posterior)

#sampling from posterior distribution
samples <- sample( p_grid , prob=posterior , size=1e5 , replace=TRUE )

#how much posterior density between 0.45 and 0.55 (ROPE)
mean(samples >= 0.45 & samples <= 0.55)

#highest-posterior density interval
HDI <- HPDI(samples, prob=.89)

HDI4 <- HDI
HDI4
#find the proportion of the HPDI that is inside the ROPE
rope(samples, range = c(.45, .55))

#credible interval
quantile(samples, c(0.025, 0.975))

plot( samples )
dens( samples , xlab="probability of choosing CS2n", show.HPDI=.89, xlim=c(0,1))
#add HPDI
#abline(v = HDI, col = "blue")
#add ROPE
abline(v = c(0.45, 0.55), col = "red")

#MAP
p_grid[ which.max(posterior) ]

mean( samples )
median( samples )

#simulate from posterior --> posterior predictive distribution
dummy_d <- rbinom( 1e5 , size=12 , prob=samples)
simplehist( dummy_d , xlab="simulated choices of CS2n" , xlim=c(0,12))
```
###ROPE for CS2n decisions using grid approximation - behav sample

```{r}
# select variables 
new_ds<- ds_behav[ which(ds_behav$CS =='4'), ]

n_choices = sum(new_ds$choices)

total_choices = sum(new_ds$total_choices)

rel_choices <- n_choices/total_choices

rel_choices*12

#grid approximation
p_grid <- seq( from=0 , to=1 , length.out=1e4 )

#mildly informative prior centered at 0.5
prior <- rnorm( 1e4, .5, .1 )
dens( prior , xlab="prior probability of choosing CS2n", xlim=c(0,1))

likelihood <- dbinom( n_choices , size=total_choices , prob=p_grid )
unstd_posterior <- prior * likelihood
posterior <- unstd_posterior / sum(unstd_posterior)

#sampling from posterior distribution
samples <- sample( p_grid , prob=posterior , size=1e5 , replace=TRUE )

#how much posterior density between 0.45 and 0.55 (ROPE)
mean(samples >= 0.45 & samples <= 0.55)

#highest-posterior density interval
HDI <- HPDI(samples, prob=.89)

HDI4 <- HDI
HDI4
#find the proportion of the HPDI that is inside the ROPE
rope(samples, range = c(.45, .55))

#credible interval
quantile(samples, c(0.025, 0.975))

plot( samples )
dens( samples , xlab="probability of choosing CS2n", show.HPDI=.89, xlim=c(0,1))
#add HPDI
#abline(v = HDI, col = "blue")
#add ROPE
abline(v = c(0.45, 0.55), col = "red")

#MAP
p_grid[ which.max(posterior) ]

mean( samples )
median( samples )

#simulate from posterior --> posterior predictive distribution
dummy_d <- rbinom( 1e5 , size=12 , prob=samples)
simplehist( dummy_d , xlab="simulated choices of CS2n" , xlim=c(0,12))
```

##raincloud plots pooled samples - Figure 1F
```{r}

w = 14
h = 7


packages <- c("ggplot2", "dplyr", "lavaan", "plyr", "cowplot", "rmarkdown", 
              "readr", "caTools", "bitops")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}


library(cowplot)
library(dplyr)
library(readr)
source("/Users/lennart/Desktop/savage/plots/rainclouds/R_rainclouds.R") #needs to be installed #https://github.com/RainCloudPlots/RainCloudPlots/tree/master/tutorial_R


# Defining the geom_flat_violin function ----

"%||%" <- function(a, b) {
  if (!is.null(a)) a else b
}

geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                             position = "dodge", trim = TRUE, scale = "area",
                             show.legend = NA, inherit.aes = TRUE, ...) {
  layer(
    data = data,
    mapping = mapping,
    stat = stat,
    geom = GeomFlatViolin,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      trim = trim,
      scale = scale,
      ...
    )
  )
}



library(scales)

library(reshape2)
my_datal <- melt(ds_wide, id.vars = c("SubID"), measure.vars = c("CS1plus", "CS2plus", "CS1n", "CS2n"), variable.name = "CS", value.name = "ChoiceProbability")

raincloud_theme = theme(
text = element_text(size = 30),
#axis.title.x = element_text(size = 16),
#axis.title.y = element_text(size = 30),
axis.title.x = element_blank(),
axis.title.y = element_blank(),
#axis.text = element_text(size = 30),
axis.text.x = element_text(color="black", 
                           size=26, angle=45, vjust = 0.5),
axis.text.y = element_text(color="black", 
                           size=26, angle=0),
axis.ticks.length.y = unit(5, "pt"),
axis.ticks.length.x = unit(0, "pt"),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=1, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=1, linetype='solid'))

lb <- function(x) mean(x) - sd(x)
ub <- function(x) mean(x) + sd(x)

sumld<- ddply(my_datal, ~CS, summarise, mean = mean(ChoiceProbability), median = median(ChoiceProbability), lower = lb(ChoiceProbability), upper = ub(ChoiceProbability))

scaleFUN <- function(x) sprintf("%.2f", x)



g <- ggplot(data = my_datal, aes(y = ChoiceProbability, x = CS, fill = CS)) +
geom_flat_violin(position = position_nudge(x = -.12, y = 0), alpha = .8, adjust =1.5) +
geom_boxplot(aes(x = as.numeric(CS)-0.12, y = ChoiceProbability), width = .1, guides = FALSE, outlier.shape = NA, alpha = .1, colour = "BLACK", size = 1.15) +
geom_point(aes(y = ChoiceProbability, color = CS, x = as.numeric(CS)-0.35),position = position_jitter(width = .12), size = 3.5, alpha = 0.5, colour = "BLACK") +
geom_hline(yintercept=0.50, linetype="dashed", 
                color = "black", size=1) +
ylab('Choice Probability')+
expand_limits(x = 4.5) +
guides(fill = FALSE) +
guides(color = FALSE) +
theme_bw() +
raincloud_theme +
scale_y_continuous(labels = scaleFUN) #+ 


# Rename / Change tick mark labels
g <- g + scale_x_discrete(breaks=c("CS1plus","CS2plus","CS1n","CS2n"),
        labels=c((expression(paste("CS"[1]^+{}, " vs ", "CS"[1]^-{}))), 
                 (expression(paste("CS"[2]^+{}, " vs ", "CS"[2]^-{}))),
                 (expression(paste("CS"[1]^n))), 
                 (expression(paste("CS"[2]^n)))))

g + scale_fill_manual(values=c("#00008B", "#6495ED", "#696969", "#D3D3D3"))

```

##raincloud plots fmri sample - Supplementary Figure 1B
```{r}

w = 14
h = 7


packages <- c("ggplot2", "dplyr", "lavaan", "plyr", "cowplot", "rmarkdown", 
              "readr", "caTools", "bitops")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}


library(cowplot)
library(dplyr)
library(readr)
source("/Users/lennart/Desktop/savage/plots/rainclouds/R_rainclouds.R")


# Defining the geom_flat_violin function ----

"%||%" <- function(a, b) {
  if (!is.null(a)) a else b
}

geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                             position = "dodge", trim = TRUE, scale = "area",
                             show.legend = NA, inherit.aes = TRUE, ...) {
  layer(
    data = data,
    mapping = mapping,
    stat = stat,
    geom = GeomFlatViolin,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      trim = trim,
      scale = scale,
      ...
    )
  )
}



library(scales)

library(reshape2)
my_datal <- melt(ds_fmri_wide, id.vars = c("SubID"), measure.vars = c("CS1plus", "CS2plus", "CS1n", "CS2n"), variable.name = "CS", value.name = "ChoiceProbability")

raincloud_theme = theme(
text = element_text(size = 30),
#axis.title.x = element_text(size = 16),
#axis.title.y = element_text(size = 30),
axis.title.x = element_blank(),
axis.title.y = element_blank(),
#axis.text = element_text(size = 30),
axis.text.x = element_text(color="black", 
                           size=26, angle=45, vjust = 0.5),
axis.text.y = element_text(color="black", 
                           size=26, angle=0),
axis.ticks.length.y = unit(5, "pt"),
axis.ticks.length.x = unit(0, "pt"),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=1, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=1, linetype='solid'))

lb <- function(x) mean(x) - sd(x)
ub <- function(x) mean(x) + sd(x)

sumld<- ddply(my_datal, ~CS, summarise, mean = mean(ChoiceProbability), median = median(ChoiceProbability), lower = lb(ChoiceProbability), upper = ub(ChoiceProbability))

scaleFUN <- function(x) sprintf("%.2f", x)



g <- ggplot(data = my_datal, aes(y = ChoiceProbability, x = CS, fill = CS)) +
geom_flat_violin(position = position_nudge(x = -.12, y = 0), alpha = .8, adjust =1.5) +
geom_boxplot(aes(x = as.numeric(CS)-0.12, y = ChoiceProbability), width = .1, guides = FALSE, outlier.shape = NA, alpha = .1, colour = "BLACK", size = 1.15) +
geom_point(aes(y = ChoiceProbability, color = CS, x = as.numeric(CS)-0.35),position = position_jitter(width = .12), size = 3.5, alpha = 0.5, colour = "BLACK") +
geom_hline(yintercept=0.50, linetype="dashed", 
                color = "black", size=1) +
ylab('Choice Probability')+
expand_limits(x = 4.5) +
guides(fill = FALSE) +
guides(color = FALSE) +
theme_bw() +
raincloud_theme +
scale_y_continuous(labels = scaleFUN) #+ 


# Rename / Change tick mark labels
g <- g + scale_x_discrete(breaks=c("CS1plus","CS2plus","CS1n","CS2n"),
        labels=c((expression(paste("CS"[1]^+{}, " vs ", "CS"[1]^-{}))), 
                 (expression(paste("CS"[2]^+{}, " vs ", "CS"[2]^-{}))),
                 (expression(paste("CS"[1]^n))), 
                 (expression(paste("CS"[2]^n)))))

g + scale_fill_manual(values=c("#00008B", "#6495ED", "#696969", "#D3D3D3"))

```
##raincloud plots behav sample  - Supplementary Figure 1A
```{r}

w = 14
h = 7


packages <- c("ggplot2", "dplyr", "lavaan", "plyr", "cowplot", "rmarkdown", 
              "readr", "caTools", "bitops")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}


library(cowplot)
library(dplyr)
library(readr)
source("/Users/lennart/Desktop/savage/plots/rainclouds/R_rainclouds.R")


# Defining the geom_flat_violin function ----

"%||%" <- function(a, b) {
  if (!is.null(a)) a else b
}

geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                             position = "dodge", trim = TRUE, scale = "area",
                             show.legend = NA, inherit.aes = TRUE, ...) {
  layer(
    data = data,
    mapping = mapping,
    stat = stat,
    geom = GeomFlatViolin,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      trim = trim,
      scale = scale,
      ...
    )
  )
}



library(scales)

library(reshape2)
my_datal <- melt(ds_behav_wide, id.vars = c("SubID"), measure.vars = c("CS1plus", "CS2plus", "CS1n", "CS2n"), variable.name = "CS", value.name = "ChoiceProbability")

raincloud_theme = theme(
text = element_text(size = 30),
#axis.title.x = element_text(size = 16),
#axis.title.y = element_text(size = 30),
axis.title.x = element_blank(),
axis.title.y = element_blank(),
#axis.text = element_text(size = 30),
axis.text.x = element_text(color="black", 
                           size=26, angle=45, vjust = 0.5),
axis.text.y = element_text(color="black", 
                           size=26, angle=0),
axis.ticks.length.y = unit(5, "pt"),
axis.ticks.length.x = unit(0, "pt"),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=1, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=1, linetype='solid'))

lb <- function(x) mean(x) - sd(x)
ub <- function(x) mean(x) + sd(x)

sumld<- ddply(my_datal, ~CS, summarise, mean = mean(ChoiceProbability), median = median(ChoiceProbability), lower = lb(ChoiceProbability), upper = ub(ChoiceProbability))

scaleFUN <- function(x) sprintf("%.2f", x)



g <- ggplot(data = my_datal, aes(y = ChoiceProbability, x = CS, fill = CS)) +
geom_flat_violin(position = position_nudge(x = -.12, y = 0), alpha = .8, adjust =1.5) +
geom_boxplot(aes(x = as.numeric(CS)-0.12, y = ChoiceProbability), width = .1, guides = FALSE, outlier.shape = NA, alpha = .1, colour = "BLACK", size = 1.15) +
geom_point(aes(y = ChoiceProbability, color = CS, x = as.numeric(CS)-0.35),position = position_jitter(width = .12), size = 3.5, alpha = 0.5, colour = "BLACK") +
geom_hline(yintercept=0.50, linetype="dashed", 
                color = "black", size=1) +
ylab('Choice Probability')+
expand_limits(x = 4.5) +
guides(fill = FALSE) +
guides(color = FALSE) +
theme_bw() +
raincloud_theme +
scale_y_continuous(labels = scaleFUN) #+ 

# Rename / Change tick mark labels
g <- g + scale_x_discrete(breaks=c("CS1plus","CS2plus","CS1n","CS2n"),
        labels=c((expression(paste("CS"[1]^+{}, " vs ", "CS"[1]^-{}))), 
                 (expression(paste("CS"[2]^+{}, " vs ", "CS"[2]^-{}))),
                 (expression(paste("CS"[1]^n))), 
                 (expression(paste("CS"[2]^n)))))

g + scale_fill_manual(values=c("#00008B", "#6495ED", "#696969", "#D3D3D3"))

```
##raincloud plots for decoding accuracy - bias vs no bias - Figure 2C
```{r}

w = 10
h = 8


packages <- c("ggplot2", "dplyr", "lavaan", "plyr", "cowplot", "rmarkdown", 
              "readr", "caTools", "bitops")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}


library(cowplot)
library(dplyr)
library(readr)
source("/Users/lennart/Desktop/savage/plots/rainclouds/R_rainclouds.R")
library(ggpubr)


# Defining the geom_flat_violin function ----

"%||%" <- function(a, b) {
  if (!is.null(a)) a else b
}

geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                             position = "dodge", trim = TRUE, scale = "area",
                             show.legend = NA, inherit.aes = TRUE, ...) {
  layer(
    data = data,
    mapping = mapping,
    stat = stat,
    geom = GeomFlatViolin,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      trim = trim,
      scale = scale,
      ...
    )
  )
}



library(scales)
library(reshape2)
my_datal <- melt(ds_decoding, id.vars = c("idx", "SubID"), measure.vars = c("Decoding_low", "Decoding_high"), variable.name = "Acc", value.name = "DecodingAcc" )


raincloud_theme = theme(
text = element_text(size = 30),
#axis.title.x = element_text(size = 16),
#axis.title.y = element_text(size = 36),
axis.title.x = element_blank(),
axis.title.y = element_blank(),
axis.text = element_text(size = 30),
axis.text.x = element_text(color="black", 
                           size=0, angle=0, vjust = 0.5),
axis.text.y = element_text(color="black", 
                           size=30, angle=0),
axis.ticks.length.y = unit(5, "pt"),
axis.ticks.length.x = unit(0, "pt"),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=1, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=1, linetype='solid'))


lb <- function(x) sd(na.omit(x)) / sqrt(29)
ub <- function(x) sd(na.omit(x)) / sqrt(29)


sumld<- ddply(my_datal, ~Acc, summarise, mean = mean(na.omit(DecodingAcc)), median = median(na.omit(DecodingAcc)), lower = lb(DecodingAcc), upper = ub(DecodingAcc))

scaleFUN <- function(x) sprintf("%.2f", x)


g <- ggplot(data = my_datal, aes(y = DecodingAcc, x = Acc, fill = Acc)) +
geom_flat_violin(position = position_nudge(x = -.10, y = 0), alpha = .8, adjust =2) +
geom_point(aes(y = DecodingAcc, color = Acc, x = as.numeric(Acc)-0.30), position = position_jitter(width = .1), size = 3.5, alpha = 0.5, colour = "BLACK") +
geom_point(data = sumld, aes(x = Acc, y = mean), position = position_nudge(-.1), colour = "BLACK", size = 4.5)+
geom_errorbar(data = sumld, aes(x = Acc, y = mean, ymin = mean-lower, ymax = mean+upper), position = position_nudge(-.1), colour = "BLACK", width = 0.1, size = 0.8)+
geom_hline(yintercept=0.5, linetype="dashed", 
                color = "black", size=1) +
expand_limits(x = 2.5) +
guides(fill = FALSE) +
guides(color = FALSE) +
theme_bw() +
raincloud_theme+
scale_y_continuous(labels = scaleFUN) #+ 


g + scale_fill_manual(values=c("#AD89BA","#892B64")) #"#AD89BA","#9D4479"

```


##raincloud plots rsa results SOC - Figure 3C
```{r}

w = 10
h = 8


packages <- c("ggplot2", "dplyr", "lavaan", "plyr", "cowplot", "rmarkdown", 
              "readr", "caTools", "bitops")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}


library(cowplot)
library(dplyr)
library(readr)
source("/Users/lennart/Desktop/savage/plots/rainclouds/R_rainclouds.R")


# Defining the geom_flat_violin function ----

"%||%" <- function(a, b) {
  if (!is.null(a)) a else b
}

geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                             position = "dodge", trim = TRUE, scale = "area",
                             show.legend = NA, inherit.aes = TRUE, ...) {
  layer(
    data = data,
    mapping = mapping,
    stat = stat,
    geom = GeomFlatViolin,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      trim = trim,
      scale = scale,
      ...
    )
  )
}



library(scales)
library(reshape2)
my_datal <- melt(ds_rsa_norm, id.vars = c("SubID"), measure.vars = c("CS2minusUSminus_early", "CS2minusUSminus_late", "CS2plusUSplus_early", "CS2plusUSplus_late"), variable.name = "CS", value.name = "PatternSimilarity")

raincloud_theme = theme(
text = element_text(size = 30),
#axis.title.x = element_text(size = 16),
axis.title.y = element_text(size = 36),
axis.title.x = element_blank(),
axis.text = element_text(size = 30),
axis.text.x = element_text(color="black", 
                           size=30, angle=45, vjust = 0.5),
axis.text.y = element_text(color="black", 
                           size=30, angle=0),
axis.ticks.length.y = unit(5, "pt"),
axis.ticks.length.x = unit(0, "pt"),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=1, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=1, linetype='solid'))

lb <- function(x) sd(x) / sqrt(29)
ub <- function(x) sd(x) / sqrt(29)


sumld<- ddply(my_datal, ~CS, summarise, mean = mean(PatternSimilarity), median = median(PatternSimilarity), lower = lb(PatternSimilarity), upper = ub(PatternSimilarity))

scaleFUN <- function(x) sprintf("%.2f", x)
my_comparisons <- list( c("CS2minusUSminus_early", "CS2minusUSminus_late"), c("CS2plusUSplus_early", "CS2plusUSplus_late"))

g <- ggplot(data = my_datal, aes(y = PatternSimilarity, x = CS, fill = CS)) +
geom_flat_violin(position = position_nudge(x = .25, y = 0), alpha = .8, adjust =2) +
#geom_boxplot(aes(x = as.numeric(CS)+0.25, y = PatternSimilarity), width = .1, guides = FALSE, outlier.shape = NA, alpha = .1, colour = "BLACK", size = 1.15) +
geom_point(aes(y = PatternSimilarity, color = CS), position = position_jitter(width = .125), size = 3.5, alpha = 0.5, colour = "BLACK") +
geom_point(data = sumld, aes(x = CS, y = mean), position = position_nudge(.25), colour = "BLACK", size = 4.5)+
geom_errorbar(data = sumld, aes(x = CS, y = mean, ymin = mean-lower, ymax = mean+upper), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.8)+
geom_hline(yintercept=0, linetype="dashed", 
                color = "black", size=1) +
xlab('CS')+ylab('Pattern Similarity')+
expand_limits(x = 4.5) +
guides(fill = FALSE) +
guides(color = FALSE) +
#scale_color_brewer(palette = "Dark2") +
#scale_fill_brewer(palette = "Dark2") +
#coord_flip() +
theme_bw() +
raincloud_theme +
scale_y_continuous(labels = scaleFUN) #+ 
#ylim(-.12, .10)


# Rename / Change tick mark labels
g <- g + scale_x_discrete(breaks=c("CS2minusUSminus_early", "CS2minusUSminus_late", "CS2plusUSplus_early", "CS2plusUSplus_late"),

        labels=c((expression(paste("CS"[2]^-{}, "-" ,"US"^-{}, "early"))),
                 (expression(paste("CS"[2]^-{}, "-" ,"US"^-{}, "late"))),
                 (expression(paste("CS"[2]^+{}, "-" ,"US"^+{}, "early"))),
                 (expression(paste("CS"[2]^+{}, "-" ,"US"^+{}, "late")))))
                                   


g + scale_fill_manual(values=c("#2A5078", "#2A5078", "#FFD653", "#FFD653"))


```


##raincloud plots rsa results FOC - Figure 3D
```{r}

w = 10
h = 8


packages <- c("ggplot2", "dplyr", "lavaan", "plyr", "cowplot", "rmarkdown", 
              "readr", "caTools", "bitops")
if (length(setdiff(packages, rownames(installed.packages()))) > 0) {
  install.packages(setdiff(packages, rownames(installed.packages())))  
}


library(cowplot)
library(dplyr)
library(readr)
source("/Users/lennart/Desktop/savage/plots/rainclouds/R_rainclouds.R")
library(ggpubr)


# Defining the geom_flat_violin function ----

"%||%" <- function(a, b) {
  if (!is.null(a)) a else b
}

geom_flat_violin <- function(mapping = NULL, data = NULL, stat = "ydensity",
                             position = "dodge", trim = TRUE, scale = "area",
                             show.legend = NA, inherit.aes = TRUE, ...) {
  layer(
    data = data,
    mapping = mapping,
    stat = stat,
    geom = GeomFlatViolin,
    position = position,
    show.legend = show.legend,
    inherit.aes = inherit.aes,
    params = list(
      trim = trim,
      scale = scale,
      ...
    )
  )
}



library(scales)
library(reshape2)
my_datal <- melt(ds_rsa_norm, id.vars = c("SubID"), measure.vars = c("CS1minusUSminus_early", "CS1minusUSminus_late", "CS1plusUSplus_early", "CS1plusUSplus_late"), variable.name = "CS", value.name = "PatternSimilarity")

raincloud_theme = theme(
text = element_text(size = 30),
#axis.title.x = element_text(size = 16),
axis.title.y = element_text(size = 36),
axis.title.x = element_blank(),
axis.text = element_text(size = 30),
axis.text.x = element_text(color="black", 
                           size=30, angle=45, vjust = 0.5),
axis.text.y = element_text(color="black", 
                           size=30, angle=0),
axis.ticks.length.y = unit(5, "pt"),
axis.ticks.length.x = unit(0, "pt"),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=1, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=1, linetype='solid'))


lb <- function(x) sd(x) / sqrt(29)
ub <- function(x) sd(x) / sqrt(29)


sumld<- ddply(my_datal, ~CS, summarise, mean = mean(PatternSimilarity), median = median(PatternSimilarity), lower = lb(PatternSimilarity), upper = ub(PatternSimilarity))

scaleFUN <- function(x) sprintf("%.2f", x)
my_comparisons <- list( c("CS1minusUSminus_early", "CS1minusUSminus_late"), c("CS1plusUSplus_early", "CS1plusUSplus_late"))

g <- ggplot(data = my_datal, aes(y = PatternSimilarity, x = CS, fill = CS)) +
geom_flat_violin(position = position_nudge(x = .25, y = 0), alpha = .8, adjust =2) +
geom_point(aes(y = PatternSimilarity, color = CS), position = position_jitter(width = .125), size = 3.5, alpha = 0.5, colour = "BLACK") +
geom_point(data = sumld, aes(x = CS, y = mean), position = position_nudge(.25), colour = "BLACK", size = 4.5)+
geom_errorbar(data = sumld, aes(x = CS, y = mean, ymin = mean-lower, ymax = mean+upper), position = position_nudge(.25), colour = "BLACK", width = 0.1, size = 0.8)+
geom_hline(yintercept=0, linetype="dashed", 
                color = "black", size=1) +
xlab('CS')+ylab('Pattern Similarity')+
expand_limits(x = 4.5) +
guides(fill = FALSE) +
guides(color = FALSE) +

theme_bw() +
raincloud_theme +
scale_y_continuous(labels = scaleFUN) #+ 

# Rename / Change tick mark labels
g <- g + scale_x_discrete(breaks=c("CS1minusUSminus_early", "CS1minusUSminus_late", "CS1plusUSplus_early", "CS1plusUSplus_late"),

        labels=c((expression(paste("CS"[1]^-{}, "-" ,"US"^-{}, "early"))),
                 (expression(paste("CS"[1]^-{}, "-" ,"US"^-{}, "late"))),
                 (expression(paste("CS"[1]^+{}, "-" ,"US"^+{}, "early"))),
                 (expression(paste("CS"[1]^+{}, "-" ,"US"^+{}, "late")))))
                                   


g + scale_fill_manual(values=c("#2A5078", "#2A5078", "#FFD653", "#FFD653"))


```


